---
title: "Chapter5"
output: html_document
---
Converting to and from Nontidy Formats
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

often text mining works with 
DTM - document-term matrix
each row represent one document
each column represents one term
each value contains the number of appearances of that term in that document.

Tidying DocumentTerMMatrix Objects
```{r}
library(tm)

data("AssociatedPress", package = "topicmodels")
AssociatedPress
```

```{r}
terms <- Terms(AssociatedPress)
head(terms)

```

```{r}
library(dplyr)
library(tidytext)

ap_td <- tidy(AssociatedPress)
ap_td

# in the tidy output the zeros (of the sparse matrix) are 
# omitted

```


```{r}
ap_sentiments <- ap_td %>%
  inner_join(get_sentiments("bing"), by = c(term = "word"))

ap_sentiments
```


```{r}
library(ggplot2)

ap_sentiments %>%
  count(sentiment, term, wt = count) %>%
  ungroup() %>%
  filter(n >= 200) %>%
  mutate(n = ifelse(sentiment == "negative", -n, n)) %>%
  mutate(term = reorder(term, n)) %>%
  ggplot(aes(term, n, fill = sentiment)) +
  geom_bar(stat = "identity") +
  ylab("Contribution to sentiment") +
  coord_flip()
```

Tidying dfm Objects
```{r}
library(methods)

data("data_corpus_inaugural", package = "quanteda")
inaug_dfm <- quanteda::dfm(data_corpus_inaugural, verbose = FALSE)

inaug_dfm

inaug_td <- tidy(inaug_dfm)
inaug_td
```


```{r}
inaug_tf_idf <- inaug_td %>%
  bind_tf_idf(term, document, count) %>% 
  arrange(desc(tf_idf))

inaug_tf_idf
```


```{r}
library(tidyr)

year_term_counts <- inaug_td %>% 
  extract(document, "year", "(\\d+)", convert = TRUE) %>% 
  complete(year, term, fill = list(count = 0)) %>% 
  group_by(year) %>% 
  mutate(year_total = sum(count))

year_term_counts %>%
  filter(term %in% c("god", "america", "foreign",
                     "union", "constitution", "freedom")) %>%
  ggplot(aes(year, count / year_total)) +
  geom_point() +
  geom_smooth() +
  facet_wrap(~ term, scales = "free_y") +
  scale_y_continuous(labels = scales::percent_format()) +
  ylab("% frequency of word in inaugural address")
```
```{r}
ap_td %>%
  cast_dtm(document, term, count)

ap_td %>%
  cast_dfm(term, document, count)
```


```{r}
library(Matrix)

# cast into a Matrix object

m <- ap_td %>% 
  cast_sparse(document, term, count)

class(m)
```


```{r}
dim(m)
```


```{r}
library(janeaustenr)

austen_dtm <- austen_books() %>% 
  unnest_tokens(word, text) %>% 
  count(book, word) %>% 
  cast_dtm(book, word, n)

austen_dtm
```

"Some data structures are designed to store document collections before tokenization, often called a "corpus"."
```{r}
data("acq")
acq[[1]]

acq_td <- tidy(acq)
acq_td
```

```{r}
acq_tokens <- acq_td %>% 
  select(-places) %>% 
  unnest_tokens(word, text) %>% 
  anti_join(stop_words, by = "word")

# most common words
acq_tokens %>% 
  count(word, sort = TRUE)

acq_tokens %>%
  count(id, word) %>%
  bind_tf_idf(word, id, n) %>%
  arrange(desc(tf_idf))
```

## Example: Mining Financial Articles
```{r}
Sys.setenv(JAVA_HOME = "
/Library/Java/JavaVirtualMachines/jdk-17.0.2.jdk/Contents/Home")
library(tm.plugin.webmining)
library(purrr)

company <- c("Microsoft", "Apple", "Google", "Amazon", "Facebook",
             "Twitter", "IBM", "Yahoo", "Netflix")
symbol <- c("MSFT", "AAPL", "GOOG", "AMZN", "FB", "TWTR", "IBM", "YHOO", "NFLX")

download_articles <- function(symbol) {
  WebCorpus(GoogleFinanceSource(paste0("NASDAQ:", symbol)))
}

# vielleicht hat google das ganze beendet
# man erreicht die webseite zumindest nicht
stock_articles <- data_frame(company = company,
                             symbol = symbol) %>%
  mutate(corpus = map(symbol, download_articles))

stock_articles
```


```{r}
stock_tokens <- stock_articles %>%
  unnest(map(corpus, tidy)) %>%
  unnest_tokens(word, text) %>%
  select(company, datetimestamp, word, id, heading)

stock_tokens
```


```{r}
library(stringr)

stock_tf_idf <- stock_tokens %>%
  count(company, word) %>%
  filter(!str_detect(word, "\\d+")) %>%
  bind_tf_idf(word, company, n) %>%
  arrange(-tf_idf)
```


```{r}
# sentiment for analysis of the stock market

# !!! AFINN, BING, NRC ARE ALL NOT SUITED FOR FINANCIAL TEXT
# DATA !!!
stock_tokens %>%
  anti_join(stop_words, by = "word") %>%
  count(word, id, sort = TRUE) %>%
  inner_join(get_sentiments("afinn"), by = "word") %>%
  group_by(word) %>%
  summarize(contribution = sum(n * score)) %>%
  top_n(12, abs(contribution)) %>%
  mutate(word = reorder(word, contribution)) %>%
  ggplot(aes(word, contribution)) +
  geom_col() +
  coord_flip() +
  labs(y = "Frequency of word * AFINN score")

```


```{r}
# use another lexicon called "loughran"
stock_tokens %>%
  count(word) %>%
  inner_join(get_sentiments("loughran"), by = "word") %>%
  group_by(sentiment) %>%
  top_n(5, n) %>%
  ungroup() %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col() +
  coord_flip() +
  facet_wrap(~ sentiment, scales = "free") +
  ylab("Frequency of this word in the recent financial articles")
```

```{r}
stock_sentiment_count <- stock_tokens %>%
  inner_join(get_sentiments("loughran"), by = "word") %>%
  count(sentiment, company) %>%
  spread(sentiment, n, fill = 0)

stock_sentiment_count

tock_sentiment_count %>%
  mutate(score = (positive - negative) / (positive + negative)) %>%
  mutate(company = reorder(company, score)) %>%
  ggplot(aes(company, score, fill = score > 0)) +
  geom_col(show.legend = FALSE) +
  coord_flip() +
  labs(x = "Company",
       y = "Positivity score among 20 recent news articles")
```

